\TheTitle

### 2017-07-05 paper/lineval.tex
Adding results section
Adding hyperref package
Renaming futurework.tex to discussion.tex
It's the whole discussion, not just futurework subsection now.
Related Works: Adding some basic related works

%% Table Support

\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{multirow}

@@

%% Graphics

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{xcolor}
\usepackage{color}
\usepackage{listings}

@@

\newcommand{\TheTitle}{An Evaluation and Generalization of Merge-Tree}
\newcommand{\TheAuthors}{Evan Wilde, Daniel M. German}
\newcommand{\TheEmails}{etcwilde@uvic.ca, dmg@uvic.ca}
\newcommand{\TheSubject}{Testing the comprehension of users in large git repositories}
\newcommand{\TheKeywords}{Linux, git, visualizations}

@@

\begin{abstract}

  \input{abstract.tex}

\end{abstract}

@@

@@

@@

\subsection{Future Work}
\label{sub:future_work}

\input{futurework.tex}

>>>>

%% Table Support
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{multirow}

@@

%% Algorithms
\usepackage{algorithm}
\usepackage{algpseudocode}

%% Graphics
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{xcolor}
\usepackage{color}
\usepackage{listings}

@@

\newcommand{\TheTitle}{Merge-Tree: Visualizing the Integration of Commits into Linux}
\newcommand{\TheAuthors}{Evan Wilde, Daniel M. German}
\newcommand{\TheEmails}{etcwilde@uvic.ca, dmg@uvic.ca}
\newcommand{\TheSubject}{Understanding a large number of commits and merges}
\newcommand{\TheKeywords}{Linux, git, visualizations}

%% Referencing
\usepackage[unicode=true,
          pdftitle={\TheTitle},
          pdfauthor={\TheAuthors},
          colorlinks=false]{hyperref}

@@

\begin{abstract}
  \input{abstract.tex}
\end{abstract}

\begin{IEEEkeywords}
  \TheKeywords
\end{IEEEkeywords}

@@

\input{relatedwork.tex}

@@

\input{results.tex}

@@

\input{discussion.tex}
